### 2016-03-22 docs/online_supporting_information.Rmd
updates table structure with master tex file

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: false
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
---

@@

Materials and methods details
-----------------------------
### Vital rate statistical models
We modeled survival probability and growth on individual genets as a function of genet size, the crowding experienced by the focal genet from both heterospecific and conspecific genets in its neighborhood (described below), temporal varation among years, and spatial variation among quadrat groups. Groups are sets of quadrats located in close proximity within a pasture or grazing exclosure).

@@

```{r make_tables, echo=FALSE, include=TRUE, results='asis', message=FALSE, eval=T, cache=FALSE, warning=FALSE}
names(vital_mat_list) <- c("growth", "survival", "recruitment")
for(do_vital in names(vital_mat_list)){
  tmp_list <- vital_mat_list[[do_vital]]
  for(do_site in names(tmp_list)){
    site_list <- tmp_list[[do_site]]
    synch_cap <- paste0("Interaction coefficients for ", do_vital, " regressions in ", do_site, ".")
    print(xtable(site_list, caption = synch_cap),
      caption.placement="top",
      include.rownames = TRUE, 
      sanitize.colnames.function = identity,
      comment=FALSE)
  }
}
```

>>>>

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
---

@@

Materials and methods details
-----------------------------
### Vital rate statistical models
We modeled survival probability and growth on individual genets as a function of genet size, the crowding experienced by the focal genet from both heterospecific and conspecific genets in its neighborhood (described below), temporal varation among years, and spatial variation among quadrat groups. Groups are sets of quadrats located in close proximity within a pasture or grazing exclosure.

@@

```{r make_tables, echo=FALSE, include=TRUE, results='asis', message=FALSE, eval=T, cache=FALSE, warning=FALSE}
names(vital_mat_list) <- c("growth", "survival", "recruitment")
for(do_vital in names(vital_mat_list)){
  tmp_list <- vital_mat_list[[do_vital]]
  for(do_site in names(tmp_list)){
    site_list <- tmp_list[[do_site]]
    synch_cap <- paste0("Interaction coefficients for ", do_vital, " regressions in ", do_site, ".")
    # digitvec <- rep(3,ncol(site_list))
    print(xtable(site_list, caption = synch_cap, digits = 4),
      caption.placement="top",
      include.rownames = TRUE, 
      sanitize.colnames.function = identity,
      comment=FALSE)
  }
}
```
